### 2014-03-26 LaTeX/RhodiumTheory.tex
Added some theory. Added map making code
Don’t use the map-making stuff yet.  It doesn’t look so great.

Laying out our hypothesis in a formal way

The guerilla group Fuerzas Armadas Revolucionarios de Colombia (FARC) appears to have to internalized these lessons.  In 1998 and 1999, the organization moved its violent operations from mostly rural areas of Colombia into major cities and near to the capital (Petras and Brescia 2000).  This coincided with economic strain caused by the implementation of an IMF/World Bank structural readjustment program.  However, the timing was likely not coincidental.  FARC advocates a number of political and economic reforms and chooses targets strategically related to these objectives.

>>>>

We suspect that substate factors will determine the economic impacts of civil conflict.  While lootable resources are often pointed to as sources of funding for rebel groups, these same resources are often critical to state economic performance.  The loss of safe access to these resources due to internal conflict should adversly affect a state's economy.  Companies that rely on the extraction of resources may find themselves unable to access those resources if armed conflict is proximately located to the resource sites.  Therefore, we expect state economic performance to be inversely related to the distance from conflict zones to valuable resources.

Other resources are also valuable to a state's ability to conduct business.  In particular, citizens must be able and willing to participate in commerce.  When major population centers are threatened by violence, residents will be less likely to engage in economically productive activities.  Violence near major population centers not only threatens residents directly, but impedes business by threatening trade between the population center and other cities or rural areas.  For this same reason, violence near important transporation hubs such as airports and sea ports should threaten business.

Finally, the perception of violence near major cities and resource centers should negatively impact foreign investment.  Investors will react negatively to news that violence is occuring near major cities and resources.  Investment is generally contingent on the expectation of a stable labor base and, sometimes, reliable access to resources.  Conflicts that appear to threaten these, whether they do or not, should correspond to a decrease in foreign investment.

These hypotheses do not seem unknown to armed actors.  The guerilla group Fuerzas Armadas Revolucionarios de Colombia (FARC) appears to have to internalized these mechanisms.  In 1998 and 1999, the organization moved its violent operations from mostly rural areas of Colombia into major cities and near to the capital (Petras and Brescia 2000).  This coincided with economic strain caused by the implementation of an IMF/World Bank structural readjustment program.  However, the timing was likely not coincidental.  FARC advocates a number of political and economic reforms and chooses targets strategically related to these objectives.
